---
title: "Final DEA"
author: "Taylor Mack"
date: "8/7/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries
The following code chunk will load all of the needed libraries used on the 
analysis

```{r}
library(plyr)
library(purrr)
library(dplyr)
library(tidyverse)
library(lubridate)
library(fixest)
```
## Setting Working Directory

In the following code chunk, will set the working directory to the "Data" folder

```{r}
setwd('./Data/')
```

## Data Sources

The following code chunk will create the various data sources for the analysis

```{r}
trend_data <- list.files(pattern = 'trends_up_to_', full.names = TRUE) %>%
           map_df(read_csv) %>%
           bind_rows()
scorecard_dict <- read_csv('./CollegeScorecardDataDictionary-09-08-2015.csv')
id_name_link <- read_csv('./id_name_link.csv')
most_recent_cohorts <- read_csv('./Most+Recent+Cohorts+(Scorecard+Elements).csv')
```
## Formatting the 'monthorweek' field

Parsing down the 'monthorweek' field from a system datetime to a yyyy-mm-dd format,
then rounding down every date to be the first of each month since the analysis is at the
yyyy-mm level. Also renaming 'monthorweek' to 'month' to be more indicative of what the data is

```{r}
trend_data$monthorweek <- str_sub(trend_data$monthorweek,1,10) %>%
                          ymd() %>%
                          floor_date(unit= 'month')
colnames(trend_data)[5] <- "month"
```

## Standardizing the index field

```{r}
trend_data <- trend_data %>% group_by(schname,keyword) %>%
              mutate(standard_index = (index - mean(index))/sd(index))
```

## Removing Colleges that have the same 'schname' value. 

```{r}
id_name_link <- group_by(id_name_link,schname) %>%
                mutate(n = n()) %>%
                filter(n = 1)
id_name_link <- id_name_link[,-4]
```

## Joining all of the datasets together

```{r}
trend_data <- inner_join(trend_data,id_name_link,by= "schname")
trend_data <- inner_join(trend_data,most_recent_cohorts,by= c("unitid"="UNITID","opeid"="OPEID"))
```

## Cleaning the datasource
  a. Adding a column that is a count of all of the rows for each month
  b. Adding a column for the month number
  c. Formatting month to no longer include the date field
  d. Adding a field to be a mirror of the student's medium wage 10 years after graduation
  e. Creating a binary field for when the scorecard went live, 0 being before 1 being after
  f. Filtered out non-numeric medium datapoints
  g. Creating a column to put incomes into "low", "medium" and "high" groupings
  h. filtered out any 'NA's that potentially were still in the dataset on the 'median_salary'
     field 

```{r}
trend_data <- trend_data %>% group_by(schname,keyword,month) %>%
               mutate(n = n()) %>%
               mutate(year = year(month)) %>%
               mutate(month_number = month(month)) %>%
               mutate(month = format(month,"%Y-%m")) %>%
               mutate(median_salary = `md_earn_wne_p10-REPORTED-EARNINGS`) %>%
               mutate(scorecard_live = case_when
               (year_month < '2015-09'~ 0,
                year_month >= '2015-09' ~ 1)) %>%
               filter(!is.na(as.numeric(median_salary))) %>%
               mutate(income_category = case_when
               (median_salary <= 30000 ~ "low",
                median_salary > 30000 &
                median_salary < 75000 ~ "medium",
                median_salary >= 75000 ~ "high")) %>%
               filter(is.na(median_salary) == FALSE)
```



## 

```{r}

```



## 

```{r}

```


## 

```{r}

```




Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
